Exoplanet population inference \& the rate of Earth analogs from noisy, incomplete catalogs

### 2014-06-01 document/ms.tex
adding arxivid for gibson paper
fixing @davidwhogg's problems with 'The Rules'

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * Sun Solar Earth all capitalized when referring to our peeps, even as in "extra-Solar"
%  * eqnarrys ONLY
%  * that is all.
%

@@

In the next \sectionname, we introduce the concept of hierarchical inference, how
it applies to the problem at hand, and we derive the importance sampling
approximation to the marginalized likelihood (this is a generalization of the
method from \citealt{hogge}).
Then, in \sect{model}, we describe how to include detection efficiencies in
this model and derive a probabilistic motivation for the standard
inverse-detection-efficiency weighting procedure.
After testing our method on synthetic catalogs in \sect{valid}, we use the
catalog of planet candidates and the empirically determined detection
efficiency from \citet{petigura} to measure the occurrence rate of Earth
analogs.

@@

\bibitem[Gibson \etal(2012)]{gibson-gp}
Gibson, N.~P., Aigrain, S., Roberts, S., \etal\ 2012, \mnras, 419, 2683

>>>>

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * Sun Solar Earth all capitalized when referring to our peeps, even as in
%    "extra-Solar"
%  * eqnarrys ONLY
%  * that is all.
%

@@

In the next Section, we introduce the concept of hierarchical inference, how
it applies to the problem at hand, and we derive the importance sampling
approximation to the marginalized likelihood (this is a generalization of the
method from \citealt{hogge}).
Then, in \sect{model}, we describe how to include detection efficiencies in
this model and derive a probabilistic motivation for the standard
inverse-detection-efficiency weighting procedure.
After testing our method on synthetic catalogs in \sect{valid}, we use the
catalog of planet candidates and the empirically determined detection
efficiency from \citet{petigura} to measure the occurrence rate of Earth
analogs.

@@

\bibitem[Gibson \etal(2012)]{gibson-gp}
Gibson, N.~P., Aigrain, S., Roberts, S., \etal\ 2012, \mnras, 419, 2683
(\arxiv{1109.3251})
